---
title: "Seeking Help from Others with reprex"
teaching: 15
exercises: 0
questions:
- "How can I get help with R from the R community?"
- "How can I get help with R from the bcgov R community?"
objectives:
- "Describe best practices for getting help from the R community."
keypoints:
- "To be able to seek help from your peers."

source: Rmd
---

## When Your Code Doesn't Work: Seeking Help from your Peers

If you're having trouble using a function or package, or getting the syntax correct, 9 times out of 10 the answers you are seeking have already been asked and answered on-line:

- [RStudio Community](https://community.rstudio.com/)
- [Stack Overflow](http://stackoverflow.com/). You can search using
the `[r]` tag.
- [Google](https://www.google.ca/)

If you can't find the answer, there are a few useful tools to
help you ask a question from your peers.

- [bcgov Yammer channels (e.g. R, Data Science CoP)](https://www.yammer.com/gov.bc.ca)
- [bcgov RocketChat #rstats channel](https://developer.gov.bc.ca/Community-and-Events/Steps-to-join-Pathfinder-Rocket.Chat#1-how-to-register-for-rocketchat)


## Help People Help You

Whan starting a conversation about code, there are a few things that when included make that conversation more efficient and pleasant for everyone:

- some sample data
- the _not-working_ code (with comments, white-space, indents `==` make it easy to read)
- information about your computing environment, like your operating system, version of R, the packages you have loaded


```{r help-dput, eval=FALSE}
?dput
```

Will dump the data you're working with into a format so that it can
be copy and pasted by anyone else into their R session.

```{r dput, eval=FALSE}
library(readr)
cats <- read_csv(file = "data/feline-data.csv")

dput(cats)

cats <- structure(list(coat = c("calico", "black", "tabby"), weight = c(2.1, 
5, 3.2), likes_string = c(1, 0, 1)), class = c("spec_tbl_df", 
"tbl_df", "tbl", "data.frame"), row.names = c(NA, -3L), spec = structure(list(
    cols = list(coat = structure(list(), class = c("collector_character", 
    "collector")), weight = structure(list(), class = c("collector_double", 
    "collector")), likes_string = structure(list(), class = c("collector_double", 
    "collector"))), default = structure(list(), class = c("collector_guess", 
    "collector")), skip = 1), class = "col_spec"))
```

```{r}
sessionInfo()
```

Will print out your current version of R, as well as any packages you
have loaded. This can be useful for others to help reproduce and debug
your issue.

## A Reproducible Example or a "reprex"

[`reprex`](https://reprex.tidyverse.org/index.html): Prepare reprexes for posting to GitHub issues, StackOverflow, Slack snippets, or email and so on.

_demo_

```{r reprex-demo1}
library(readr)
library(dplyr)
library(ggplot2)

cats <- read_csv(file = "data/feline-data.csv")

cats %>% 
  select(coat, weight) %>% 
  ggplot(aes(x = coat, y = weight)) +  
  geom_col()

# Make bar chart - this does not work?
cats %>% 
  select(coat, weight) %>% 
  ggplot(aes(x = coat, y = weight)) %>%   
  geom_col()
```

I have used `?ggplot2` and looked on-line and cannot find an answer. Maybe someone in the bcgovR community knows? 

We need to invest a bit of time making the buggy code shareable.


```{r reprex-demo2}
library(readr)
library(dplyr)
library(ggplot2)


cats <- structure(list(coat = c("calico", "black", "tabby"), weight = c(2.1, 
5, 3.2), likes_string = c(1, 0, 1)), class = c("spec_tbl_df", 
"tbl_df", "tbl", "data.frame"), row.names = c(NA, -3L), spec = structure(list(
    cols = list(coat = structure(list(), class = c("collector_character", 
    "collector")), weight = structure(list(), class = c("collector_double", 
    "collector")), likes_string = structure(list(), class = c("collector_double", 
    "collector"))), default = structure(list(), class = c("collector_guess", 
    "collector")), skip = 1), class = "col_spec"))


cats %>% 
  select(coat, weight) %>% 
  ggplot(aes(x = coat, y = weight)) %>%  
  geom_col()
```

```{r reprex-demo}
library(readr)
library(dplyr)
library(ggplot2)


cats <- read_csv(file = "data/feline-data.csv")

dput(cats)

cats %>% 
  select(coat, weight) %>% 
  ggplot(aes(x = coat, y = weight)) %>%  
  geom_col()


starwars %>% 
  select(name, height) %>% 
  ggplot(aes(x = name, y = height)) %>%  
  geom_col()

```

## Other Helpful Resources

* [RStudio cheat sheets](http://www.rstudio.com/resources/cheatsheets/)
* [Quick R](http://www.statmethods.net/)
* [Cookbook for R](http://www.cookbook-r.com/)

